Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
A suggestion
Fix typo
Remove redundant sentence.
adding text and bytestring to support observation.

\begin{itemize}
\item
    We originally implemented Doctest and
    extended Haddock's markup to support examples, back in 2010
\item
    Add support for QuickCheck properties to Doctest and
    extend Haddock markup to support properties
    (Section
    \ref{sec:user-doc} and Section \ref{sec:doctest})

@@

For Doctest, we should use Haddock markup to express evidence.
Haddock has markup support for code blocks.  And it is widely used to
include properties and examples in documentation.
For instance, the {\tt filepath} package and
the {\tt containers} package adopt this style.
Here is an example from the latter.

>>>>

\begin{itemize}
\item
    We originally implemented Haskell's version of Doctest, and extended
    Haddock's markup to support examples, back in 2010
\item
    Add support for QuickCheck properties to Doctest and
    extend Haddock markup to support properties
    (Section
    \ref{sec:user-doc} and Section \ref{sec:doctest})

@@

Haddock has markup support for code blocks.  And it is widely used to
include properties and examples in documentation.
For instance, some packages, including {\tt filepath}, 
{\tt containers}, {\tt bytestring} and {\tt text}, adopt this style.
Here is an example from the latter.
